Tabsets

### 2024-04-27 index.qmd
abc

>>>>

```{mermaid}
%% R/wasmconverting.R
%%| echo: false
classDiagram
    note for abc "a"
    note for cde "b"
    note for fgh "c"
    class SimVoterdatabase{
        +field1
        +abc1()
    }
    class Abc{
        +field1
        +abc1()
    }
    class Def{
        +field1
        +abc1()
    }
    class Ghi{
        +field1
        +abc1()
    }
    Initmodelnum --|> Abc
    Initmodelnum --|> Def
    Initmodelnum --|> Ghi
```

```{mermaid}
%% R/wasmconverting.R
%% Countinggraphs 
%%| echo: false
classDiagram
    note for abc "a"
    note for cde "b"
    note for fgh "c"
    class Countingprocess{
        +field1
        +abc1()
    }
    class Abc{
        +field1
        +abc1()
    }
    class Def{
        +field1
        +abc1()
    }
    class Ghi{
        +field1
        +abc1()
    }
    Initmodelnum --|> Abc
    Initmodelnum --|> Def
    Initmodelnum --|> Ghi
    class Countinggraphs{
        +field1
        +abc1()
    }
```

```{mermaid}
%% R/wasmconverting.R
%% Countinggraphs 
%%| echo: false
classDiagram
    note for abc "a"
    note for cde "b"
    note for fgh "c"
    class Estimation{
        +field1
        +abc1()
    }
    class Abc{
        +field1
        +abc1()
    }
    class Def{
        +field1
        +abc1()
    }
    class Ghi{
        +field1
        +abc1()
    }
    Initmodelnum --|> Abc
    Initmodelnum --|> Def
    Initmodelnum --|> Ghi
```
